### 2021-09-17 plos_latex_template.tex
Several changes in rules + reorganization + comments :see_no_evil: (~Rocío, Andrea, Yani, Marce, Sara)

While it is essential to improve representation towards some of the most visible dimensions of human diversity, such as race, gender, and country of origin, building a truly inclusive environment means taking care of all the other aspects of diversity as well. Having consideration of religious practices, setting specific accommodations for breastfeeding and child care, having LGBTQIA+-friendly spaces, creating community-only spaces, enforcing the use of pronouns, and treating gender as a non-binary variable are just some examples of decisions that can make inclusion real.
% Rocío: I'm not sure if "variable" is the right term for non-binary since this is not a statistical analysis but real life.
Intersectionality also needs to be taken into account, to address multiple inequalities and barriers to unprivileged people that intersect and interact with each other \cite{crenshaw1989}. Importantly, you can take active steps in creating a more welcoming environment without requiring anyone to disclose personal information.

>>>>

While it is essential to improve representation towards some of the most visible dimensions of human diversity, such as race, gender, and country of origin, building a truly inclusive environment means taking care of all the other aspects of diversity as well. Having consideration of religious practices, setting specific accommodations for breastfeeding and child care, having LGBTQIA+-friendly spaces, creating community-only spaces, enforcing the use of pronouns, and acknowledging gender is not binary  are just some examples of decisions that can make inclusion real.
Intersectionality also needs to be taken into account, to address multiple inequalities and barriers to unprivileged people that intersect and interact with each other \cite{crenshaw1989}. Importantly, you can take active steps in creating a more welcoming environment without requiring anyone to disclose personal information.
